Accurate binding of sodium and calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-11-01 Manuscript/manuscript.tex
Corrected/Added APL extra values.

\begin{table}
  \caption{Area per lipid (APL) values of POPC bilayer without ions from the Lipid14 simulation
    ran in this work and from the literature, from the ECC-lipid model and from experiments.\label{tab:apls} }
  \begin{tabular}{l|c c}
    model          & APL (\AA$^2$)   & Temperature [K] \\
    \hline
    Lipid14                   & 65.1$\pm$ 0.6  &  300 \\
    Lipid14 \cite{dickson14}  & 65.6$\pm$ 0.5  &  303 \\
    \hline
    ECC-lipids                & 62.2$\pm$ 0.6  &  300       \\
    \hline
    experiment \cite{kucerka11} & 64.3  &  303    \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{Area per lipid (APL) from different models of POPC with no ions\label{tab:apls_si} }
  \begin{tabular}{l|c c}
    model          & APL (\AA$^2$)   & Temperature [K] \\
    \hline
    Lipid14                   & 65.1$\pm$ 0.6  &  300 \\
    Lipid14 \cite{dickson14}  & 65.6$\pm$ 0.5  &  303 \\
    \hline
    ECC-lipids &        &  \\
    %Lipid14ecc0.80+sigma0.875 &        &  313    \\
    %($4.6\cdot 5.1 \, \mathrm{nm}^2$), 72 lipids patch, OPC3           & 63.2   &   313      \\
    ~ OPC3           & 62.2$\pm$ 0.6   &  300       \\
    ~ OPC3           & 64.2$\pm$ 0.6   &  313       \\
    ~ SPC/E          & 65.1$\pm$ 0.6   &  313       \\
    ~ OPC            & 64.4$\pm$ 0.6   &  313       \\
    ~ TIP4p/2005     & 66.8$\pm$ 0.6   &  313       \\
    %($9.2\cdot 10.2 \, \mathrm{nm}^2$), 288 lipids patch           & 65.5   &  313       \\ %% not done for this model with f_sigma=0.89
    %oMM small patch           & 63.65  &         \\
    %oMM 4xbig patch           & 63.7   &         \\
    \hline
    experiment   & 62.7  &  293    \\
    experiment \cite{kucerka11} & 64.3  &  303    \\
    experiment  & 67.3  &  323    \\
    experiment  & 68.1  &  333    \\
    %experiment POPE  & 56.6 &  303    \\
    \hline
  \end{tabular} \\
  \todo{Result with normal TIP3P missing?}
\end{table}

>>>>

\begin{table}
  \caption{Area per lipid (APL) values of POPC bilayer without ions from the Lipid14 simulation
    ran in this work and from the literature, from the ECC-lipid model and from experiments.\label{tab:apls} }
  \begin{tabular}{l|c c}
    model          & APL (\AA$^2$)   & Temperature [K] \\
    \hline
    Lipid14                   & 65.1$\pm$ 0.6  &  300 \\
    Lipid14 \cite{dickson14}  & 65.6$\pm$ 0.5  &  303 \\
    \hline
    ECC-lipids                & 63.2$\pm$ 0.6  &  300       \\
    \hline
    experiment \cite{kucerka11} & 64.3  &  303    \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{Area per lipid (APL) from different models of POPC with no ions\label{tab:apls_si} }
  \begin{tabular}{l|c c}
    model          & APL (\AA$^2$)   & Temperature [K] \\
    \hline
    Lipid14                   & 65.1$\pm$ 0.6  &  300 \\
    Lipid14 \cite{dickson14}  & 65.6$\pm$ 0.5  &  303 \\
    \hline
    ECC-lipids &        &  \\
    %Lipid14ecc0.80+sigma0.875 &        &  313    \\
    %($4.6\cdot 5.1 \, \mathrm{nm}^2$), 72 lipids patch, OPC3           & 63.2   &   313      \\
    ~ OPC3           & 62.2$\pm$ 0.6   &  300       \\
    ~ OPC3           & 64.2$\pm$ 0.6   &  313       \\
    ~ SPC/E          & 65.1$\pm$ 0.6   &  313       \\
    ~ SPC/E          & 63.2$\pm$ 0.6   &  300       \\
    ~ OPC            & 64.4$\pm$ 0.6   &  313       \\
    ~ TIP4p/2005     & 66.8$\pm$ 0.6   &  313       \\
    ~ TIP3p          & 66.2$\pm$ 0.6   &  313       \\
    ~ TIP3p-FB       & 64.8$\pm$ 0.6   &  313       \\
    ~ TIP4p-FB       & 65.6$\pm$ 0.6   &  313       \\
    %($9.2\cdot 10.2 \, \mathrm{nm}^2$), 288 lipids patch           & 65.5   &  313       \\ %% not done for this model with f_sigma=0.89
    %oMM small patch           & 63.65  &         \\
    %oMM 4xbig patch           & 63.7   &         \\
    \hline
    experiment   & 62.7  &  293    \\
    experiment \cite{kucerka11} & 64.3  &  303    \\
    experiment  & 67.3  &  323    \\
    experiment  & 68.1  &  333    \\
    %experiment POPE  & 56.6 &  303    \\
    \hline
  \end{tabular} \\
  \todo{Result with normal TIP3P missing?}
\end{table}
